\documentclass[11pt]{article}

\usepackage{graphicx}
\usepackage{color}
\usepackage{epstopdf}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{dsfont}
\usepackage{geometry, textcomp}
\usepackage{paralist}

%\input{header.tex}
\renewcommand{\familydefault}{\sfdefault}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% For A4 paper
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \geometry{paperwidth = 210 mm, paperheight = 297 mm, left = 20 mm,
% right = 20 mm, top = 20 mm, bottom = 20 mm}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% For letter paper
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\geometry{left = 0.85 in, right = 0.85 in, top = 0.75 in, bottom = 0.75 in}

%\geometry{left = 0.85 in, right = 0.85 in, top = 0.5 in, bottom = 0.5 in}


% Paragraph spacing
\parskip = 0.1 in

% Paragraph indenting
\parindent = 0.0 in

% Default to Sans Serif font
\renewcommand{\familydefault}{\sfdefault}

%% No page numbers
 \pagestyle{empty}

% Set custom widths
%\newcommand{\parwidth}{4.8 in}
\newcommand{\parwidth}{5.3 in}
%\newcommand{\pagewidth}{6.5 in}
\newcommand{\pagewidth}{6.8 in}
%\newcommand{\tabwidth}{2.0 in}
\newcommand{\tabwidth}{1.5 in}
\newcommand{\parwidthNarrow}{4.8 in}
\newcommand{\tabwidthWide}{2.0 in}

\def\labelitemi{--}

% Section heading
\newcommand{\head}[1]{
{\bf #1} \\
\rule{\textwidth}{0.01 in}

\vspace{-0.35 in}

}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Begin Document
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title{}
\author{}
\date{}
\begin{document}
%% \maketitle{}

% \input{../covers/}
%\newpage


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Header
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{center}{\Huge KRISTAL CURTIS} \end{center}
\rule{\textwidth}{0.01 in}

\begin{minipage}{0.5 \textwidth}
\begin{flushleft}
Graduate Student Researcher \\
EECS Department\\
University of California, Berkeley \\
www.eecs.berkeley.edu/$\sim$kcurtis
\ 
\end{flushleft}
\end{minipage}
\begin{minipage}{0.5 \textwidth}
\begin{flushright}
924 Chenery Street\\
San Francisco, CA 94131\\
702.592.1110\\
kcurtis@eecs.berkeley.edu\\
\end{flushright}
\end{minipage}
%\vspace{0.25 in}
\vspace{0.1 in}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Education
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\head{Education}

\begin{tabbing}
\hspace{\tabwidthWide} \= \\ 

December 2015 (expected) \> \emph{Ph.D. in Computer Science}, University of California, Berkeley \\ 
December 2010 \> \emph{M.S. in Computer Science}, University of California, Berkeley \\ 
\> \parbox[t]{\parwidthNarrow}{Advisors: David Patterson and Armando Fox } \\ 
\> \parbox[t]{\parwidthNarrow}{Major in Artificial Intelligence} \\
\> \parbox[t]{\parwidthNarrow}{Minors in Systems and Statistics} \\
\> \parbox[t]{\parwidthNarrow}{Graduate GPA: 3.76} \\ \\

May 2007 \> \emph{B.S. in Computer Science}, University of Nevada, Las Vegas \\ 
\> \emph{B.S. in Electrical Engineering}, University of Nevada, Las Vegas \\ 
\> \parbox[t]{\parwidthNarrow}{Minor in Mathematics} \\
\> \parbox[t]{\parwidthNarrow}{Undergraduate GPA: 3.98} \\ \\

Research Interests \> \parbox[t]{\parwidthNarrow}{
Large-Scale Distributed Systems, Data Science, Cloud Computing, Machine Learning, Genomics, Performance Modeling, Scalable Storage
} \\

\end{tabbing}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Research Activities
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\head{Research}

\begin{tabbing}
\hspace{\tabwidth} \= \\ 

\parbox[t]{\pagewidth}{\textbf{Kristal Curtis}, Ameet Talwalkar, Matei Zaharia, Armando Fox, and David Patterson.  ``SiRen:  Leveraging Similar Regions for Efficient \& Accurate Variant Calling."  Technical Report No. UCB/EECS-2015-159, 2015.}\\ \\
\parbox[t]{\pagewidth}{Ameet Talwalkar, Jesse Liptrap, Julie Newcomb, Christopher Hartl, Jonathan Terhorst, \textbf{Kristal Curtis}, Ma'ayan Bresler, Yun S. Song, Michael I. Jordan, and David Patterson.  ``SMaSH:  a benchmarking toolkit for human genome variant calling."  Bioinformatics, Vol. 30, No. 19, pp. 2787--2795, 2014.}\\ \\
\parbox[t]{\pagewidth}{Durga Kandasamy, \textbf{Kristal Curtis}, Armando Fox, and David Patterson.  ``Using Diversity within the Crowd."  Poster and extended abstract at the ACM Conference on Computer Supported Collaborative Work (CSCW), 2012.}\\ \\
\parbox[t]{\pagewidth}{Matei Zaharia, William J. Bolosky, \textbf{Kristal Curtis}, Armando Fox, David Patterson, Scott Shenker, Ion Stoica, Richard Karp, and Taylor Sittler.  ``Faster and More Accurate Sequence Alignment with SNAP."  ArXiv Technical Report 1111.5572v1, 2011.}\\ \\
\parbox[t]{\pagewidth}{Michael Armbrust, \textbf{Kristal Curtis}, Tim Kraska, Armando Fox, Michael J. Franklin, and David Patterson.  ``PIQL:  Success-Tolerant Query Processing in the Cloud."  Proceedings of the Very Large Data Bases Endowment Inc. (VLDB Endowment), Vol. 5, No. 3, 2011.}\\ \\
\parbox[t]{\pagewidth}{\textbf{Kristal Curtis}.  ``Determining SLO Violations at Compile Time."  M.S. Thesis, UC Berkeley, 2010.}\\ \\
\parbox[t]{\pagewidth}{\textbf{Kristal Curtis}, Peter Bod\'{i}k, Michael Armbrust, Armando Fox, Michael Jordan, and David Patterson.  ``Determining SLO Violations at Compile Time."  Work-In-Progress talk and poster at the 8th USENIX Conference on File and Storage Technologies (FAST), 2010.}\\ \\
\parbox[t]{\pagewidth}{\textbf{Kristal Curtis}, Peter Bod\'{i}k, Archana Ganapathi, Armando Fox, Michael Jordan, and David Patterson.  ``Combining Queueing-theoretic and Statistical Techniques for Modeling the Impact of Dynamic Workload Mixes on Web 2.0 Service Times."  Poster at the 22nd ACM Symposium on Operating Systems Principles (SOSP), 2009.}\\
%\parbox[t]{\pagewidth}{"Automatic Workload Evaluation (AWE):  Characterizing Web 2.0 Workload Behavior."  Invited talk at Microsoft Research (MSR) Redmond, May 2009.}\\ \\
\end{tabbing}

%\pagebreak

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Employment
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\head{Employment}

\begin{tabbing}
\hspace{\tabwidth} \= \\ 
2011 - 2015 \> \parbox[t]{\parwidth}{\textit{Graduate Researcher in the Algorithms, Machines, and People (AMP) Lab},}\\
\> \parbox[t]{\parwidth}{University of California, Berkeley}\\
\> \parbox[t]{\parwidth}{
\begin{compactitem}
\item Designed and implemented distributed algorithms to recognize and deploy specialized processing on difficult regions of the genome (SiRen) using Scala \& Spark
\item Contributed to a benchmarking framework for genomics algorithms (SMaSH)
\item Developed a short-read alignment algorithm for DNA sequencing data (SNAP) using Scala
\end{compactitem}
} \\

\hspace{\tabwidth} \= \\ 
2008 - 2011 \> \parbox[t]{\parwidth}{\textit{Graduate Researcher in the Reliable, Adaptive, Distributed (RAD) Lab},}\\
\> \parbox[t]{\parwidth}{University of California, Berkeley}\\
\> \parbox[t]{\parwidth}{
\begin{compactitem}
\item Designed modeling infrastructure for database query service level objective (SLO) compliance prediction using Scala \& R
\item Built performance models for three-tier web 2.0-style apps using R
\end{compactitem}
}\\

\hspace{\tabwidth} \= \\ 
June - August 2008 \> \emph{Software Engineering Intern in Search Quality}, Google, Mountain View, CA \\ 
\> \parbox[t]{\parwidth}{
\begin{compactitem}
\item Designed a machine learning algorithm for handling ambiguous search queries
\item Built a MapReduce pipeline using C++ that ran on O(1,000)-node clusters
\end{compactitem}
}\\

\hspace{\tabwidth} \= \\ 
2003 - 2007 \> \emph{Undergraduate Researcher}, University of Nevada, Las Vegas \\ 
\> \parbox[t]{\parwidth}{
\begin{compactitem}
\item Developed gesture recognition algorithms for robot vision using C++ via Windows Visual Studio
\end{compactitem}
}\\

\end{tabbing}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Teaching Experience 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\head{Teaching Experience}

\begin{tabbing}
\hspace{\tabwidth} \= \\

Fall 2010 \> \emph{Teaching Assistant for Software Engineering}\\
\> \parbox[t]{\parwidth}{Computer Science Division, University of California, Berkeley} \\ 
\> \parbox[t]{\parwidth}{Led discussion sections and supervised project teams for course on developing software as a service (SaaS) applications using Ruby on Rails \& cloud computing} \\ \\

Spring 2010 \> \emph{Teaching Assistant for Software Engineering} \\
\> \parbox[t]{\parwidth}{Computer Science Division, University of California, Berkeley} \\ 
\> \parbox[t]{\parwidth}{Supervised project teams for course on developing mobile applications for iOS \& Android} \\ 

\end{tabbing}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Honors and Awards 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\head{Honors and Awards}

\begin{tabbing}
\hspace{\tabwidth} \= \\

2011 \> \emph{Facebook Grace Hopper Women in Computing Scholarship}\\ \\

2008 \> \emph{National Science Foundation Graduate Research Fellowship} \\ \\

2007 \> \emph{Chancellor's Fellowship}, University of California, Berkeley \\ \\

2007 \> \emph{Graduated Summa Cum Laude}, University of Nevada, Las Vegas \\ \\
\end{tabbing}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Outreach and Other Activities 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\head{Outreach}

\begin{tabbing}
\hspace{\tabwidth} \= \\

2010 - 2013 \> \emph{Mentor to Undergraduate Researchers}\\
\> \parbox[t]{\parwidth}{
\begin{compactitem}
\item Designed crowdsourcing and genomics projects
\item Supervised three student researchers
\end{compactitem}
} \\ \\

2009 - 2011 \> \emph{Leadership for Women in Computer Science and Engineering (WICSE)} \\
\> \parbox[t]{\parwidth}{
\begin{compactitem}
\item Organized weekly networking events
\item Recruited and supervised volunteers to participate in events
\end{compactitem}
} \\

\end{tabbing}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Service
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\head{Service}

\begin{tabbing}
\hspace{\tabwidth} \= \\
%\parbox[t]{\pagewidth}{Program Committee, The First International Workshop on Hot Topics in Big Data and Networking (HotData I) 2014}\\ \\
2014 \> \parbox[t]{\parwidth}{Program Committee, The First International Workshop on Hot Topics in Big Data and Networking (HotData I)}\\ \\
%\parbox[t]{\pagewidth}{Reviewer, Symposium on Operating Systems Principles (SOSP) 2013}\\ \\
2013 \> \parbox[t]{\parwidth}{Reviewer, Symposium on Operating Systems Principles (SOSP)}\\ \\
%\parbox[t]{\pagewidth}{Program Committee, Managing Large-Scale Systems via the Analysis of System Logs and the Application of Machine Learning Techniques (SLAML) 2011}\\ \\
2011 \> \parbox[t]{\parwidth}{Program Committee, Managing Large-Scale Systems via the Analysis of System Logs and the Application of Machine Learning Techniques (SLAML)}\\ \\
2011 \> \parbox[t]{\parwidth}{Reviewer, IEEE Transactions on Network and Service Management}\\ \\
2010 \> \parbox[t]{\parwidth}{Reviewer, Elsevier Computer Networks Journal}

\end{tabbing}

\end{document}

