\documentclass[11pt]{article}

\usepackage{graphicx}
\usepackage{color}
\usepackage{epstopdf}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{dsfont}
\usepackage{geometry, textcomp}

%\input{header.tex}
\renewcommand{\familydefault}{\sfdefault}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% For A4 paper
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \geometry{paperwidth = 210 mm, paperheight = 297 mm, left = 20 mm,
% right = 20 mm, top = 20 mm, bottom = 20 mm}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% For letter paper
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\geometry{left = 0.85 in, right = 0.85 in, top = 0.75 in, bottom =
%  0.75 in}

\geometry{left = 0.85 in, right = 0.85 in, top = 0.5 in, bottom =
  0.5 in}


% Paragraph spacing
\parskip = 0.1 in

% Paragraph indenting
\parindent = 0.0 in

% Default to Sans Serif font
\renewcommand{\familydefault}{\sfdefault}

%% No page numbers
 \pagestyle{empty}

% Set custom widths
\newcommand{\parwidth}{4.8 in}
\newcommand{\pagewidth}{6.5 in}
\newcommand{\tabwidth}{2.0 in}

% Section heading
\newcommand{\head}[1]{
{\bf #1} \\
\rule{\textwidth}{0.01 in}

\vspace{-0.35 in}

}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Begin Document
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title{}
\author{}
\date{}
\begin{document}
%% \maketitle{}

% \input{../covers/}
%\newpage


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Header
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{center}{\Huge KRISTAL CURTIS} \end{center}
\rule{\textwidth}{0.01 in}

\begin{minipage}{0.5 \textwidth}
\begin{flushleft}
Graduate Student Researcher \\
EECS Department\\
University of California, Berkeley \\
www.eecs.berkeley.edu/$\sim$kcurtis
\ 
\end{flushleft}
\end{minipage}
\begin{minipage}{0.5 \textwidth}
\begin{flushright}
180 Brannan St. \#311 \\
San Francisco, CA 94107 \\
702.592.1110\\
kcurtis@eecs.berkeley.edu\\
\end{flushright}
\end{minipage}
%\vspace{0.25 in}
\vspace{0.1 in}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Education
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\head{Education}

\begin{tabbing}
\hspace{\tabwidth} \= \\ 

May 2014 (Expected) \> \emph{Ph.D. in Computer Science, University of California, Berkeley} \\ 
December 2010 \> \emph{M.S. in Computer Science, University of California, Berkeley} \\ 
\> \parbox[t]{\parwidth}{Advisors: David Patterson and Armando Fox } \\ 
\> \parbox[t]{\parwidth}{Major in Artificial Intelligence} \\
\> \parbox[t]{\parwidth}{Minors in Systems and Statistics} \\
\> \parbox[t]{\parwidth}{Graduate GPA: 3.76} \\ \\

May 2007 \> \emph{B.S. in Computer Science, University of Nevada, Las Vegas} \\ 
\> \emph{B.S. in Electrical Engineering, University of Nevada, Las Vegas} \\ 
\> \parbox[t]{\parwidth}{Minor in Mathematics} \\
\> \parbox[t]{\parwidth}{Undergraduate GPA: 3.98} \\ \\

Research Interests \> \parbox[t]{\parwidth}{
Large-Scale Distributed Systems, Cloud Computing, Machine Learning, Performance Modeling, Scalable Storage, Crowdsourcing, Genomics
} \\

\end{tabbing}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Research Activities
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\head{Research}

\begin{tabbing}
\hspace{\tabwidth} \= \\ 

\parbox[t]{\pagewidth}{Durga Kandasamy, Kristal Curtis, Armando Fox, and David Patterson.  "Using Diversity within the Crowd."  Poster and extended abstract at the 2012 ACM Conference on Computer Supported Collaborative Work (CSCW 2012).}\\ \\
\parbox[t]{\pagewidth}{Matei Zaharia, William J. Bolosky, Kristal Curtis, Armando Fox, David Patterson, Scott Shenker, Ion Stoica, Richard Karp, and Taylor Sittler.  "Faster and More Accurate Sequence Alignment with SNAP."  ArXiv Technical Report 1111.5572v1, Nov. 2011.}\\ \\
\parbox[t]{\pagewidth}{Michael Armbrust, Kristal Curtis, Tim Kraska, Armando Fox, Michael J. Franklin, and David A. Patterson.  "PIQL:  Success-Tolerant Query Processing in the Cloud."  Proceedings of the Very Large Data Bases Endowment Inc. (VLDB Endowment), Vol. 5, No. 3, 2011.}\\ \\
\parbox[t]{\pagewidth}{Kristal Curtis.  "Determining SLO Violations at Compile Time."  MS Thesis, UC Berkeley, December 2010.}\\ \\
\parbox[t]{\pagewidth}{Kristal Curtis, Peter Bod\'{i}k, Michael Armbrust, Armando Fox, Michael Jordan, and David Patterson.  "Determining SLO Violations at Compile Time."  Work-In-Progress talk and poster at the 8th USENIX Conference on File and Storage Technologies (FAST 2010).}\\ \\
\parbox[t]{\pagewidth}{Kristal Curtis, Peter Bod\'{i}k, Archana Ganapathi, Armando Fox, Michael Jordan, and David Patterson.  "Combining Queueing-theoretic and Statistical Techniques for Modeling the Impact of Dynamic Workload Mixes on Web 2.0 Service Times."  Poster at the 22nd ACM Symposium on Operating Systems Principles (SOSP 2009).}\\
%\parbox[t]{\pagewidth}{"Automatic Workload Evaluation (AWE):  Characterizing Web 2.0 Workload Behavior."  Invited talk at Microsoft Research (MSR) Redmond, May 2009.}\\ \\
\end{tabbing}

\pagebreak

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Employment
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\head{Employment}

\begin{tabbing}
\hspace{\tabwidth} \= \\ 
March 2008 - Present \> \emph{Graduate Researcher, University of California, Berkeley} \\ 
\> \parbox[t]{\parwidth}{
Researching performance modeling for scalable storage, genomics
}\\

\hspace{\tabwidth} \= \\ 
June 2008 - August 2008 \> \emph{Software Engineering Intern, Google, Mountain View, CA} \\ 
\> \parbox[t]{\parwidth}{
Worked on Search Quality team developing approaches for handling ambiguous entities
}\\

\hspace{\tabwidth} \= \\ 
June 2003 - June 2007 \> \emph{Undergraduate Researcher, University of Nevada, Las Vegas} \\ 
\> \parbox[t]{\parwidth}{
Researched robot vision for telecontrolled scientific experiments
}\\

\end{tabbing}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Teaching Experience 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\head{Teaching Experience}

\begin{tabbing}
\hspace{\tabwidth} \= \\

Fall 2010 \> \emph{Teaching Assistant for Software Engineering}\\
\> \parbox[t]{\parwidth}{Department of Computer Science, University of California, Berkeley} \\ 
\> \parbox[t]{\parwidth}{Course focused on developing software as a service (SaaS) applications using Ruby on Rails and cloud computing} \\ \\

Spring 2010 \> \emph{Teaching Assistant for Software Engineering} \\
\> \parbox[t]{\parwidth}{Department of Computer Science, University of California, Berkeley} \\ 
\> \parbox[t]{\parwidth}{Course focused on developing mobile applications for iOS and Android} \\ 

\end{tabbing}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Honors and Awards 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\head{Honors and Awards}

\begin{tabbing}
\hspace{\tabwidth} \= \\

2011 \> \emph{Facebook Grace Hopper Women in Computing Scholarship}\\ \\

2008 \> \emph{National Science Foundation Graduate Research Fellowship} \\ \\

2007 \> \emph{Chancellor's Fellowship, University of California, Berkeley} \\ \\

2007 \> \emph{Graduated Summa Cum Laude, University of Nevada, Las Vegas} \\ \\
\end{tabbing}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Outreach and Other Activities 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\head{Outreach}

\begin{tabbing}
\hspace{\tabwidth} \= \\

Summer 2010 - Present \> \emph{Mentor to Undergraduate Researchers}\\ \\

Summer 2009 - Spring 2011 \> \emph{Leadership for Women in Computer Science and Engineering (WICSE)} \\
\end{tabbing}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Service
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\head{Service}

\begin{tabbing}
\hspace{\tabwidth} \= \\

\parbox[t]{\pagewidth}{Program Committee, Managing Large-Scale Systems via the Analysis of System Logs and the Application of Machine Learning Techniques (SLAML 2011)}\\ \\
\parbox[t]{\pagewidth}{Reviewer, IEEE Transactions on Network and Service Management}\\ \\
\parbox[t]{\pagewidth}{Reviewer, Elsevier Computer Networks Journal}

\end{tabbing}

\end{document}

